Bayesian Data Analysis - Rough Draft

### 2023-11-30 Lahman Analysis/Formal Analysis/Draft 1.qmd
Literally just added one sentance
Added a player trajectory

library(tidyverse)
library(rstan)
library(Lahman)
library(bayesplot)
library(corrplot)
```

@@

#Create a centered age variable by subtracting 30 from everyone's age

Batting <- Batting %>% 
  mutate(cAge = Age -30, .after = Age)
```

@@

In this model, we say that the $HR$'s of player $n$ are binomialy distributed with number of trials for player $n$ are $AB$. The probability of success (hitting a HR) denoted as $\pi$. Furthermore, we measure $\pi$ on the logistic scale. It is obvious from the model that $\pi$ changes due to a variety of factors.

@@

>>>>

library(tidyverse)
library(rstan)
library(Lahman)
library(bayesplot)
library(tidybayes)
library(corrplot)
```

@@

#Create a centered age variable by subtracting 30 from everyone's age and square it for non-liner effect

Batting <- Batting %>% 
  mutate(cAge = Age -30, .after = Age) %>% 
  mutate(cAgeSq = cAge**2, .after = cAge)

#Make a year index because it's easier than having to create one everytime

Batting <- Batting %>% 
  mutate(year_index = yearID -1972, .after = yearID)
```

@@

In this model, we say that the $HR$'s of player $n$ are binomialy distributed with number of trials for player $n$ are $AB$. The probability of success (hitting a HR) denoted as $\pi$. Furthermore, we measure $\pi$ on the logistic scale. It is obvious from the model that $\pi$ changes due to a variety of factors. The first parameter which affects $\pi$ is $\alpha_n$.

@@

```{r}
#The selected player (id=651) is Robin Yount

set.seed(1)

select_player <- Batting %>% 
  distinct(playerID) %>% 
  pull(playerID) %>% 
  sample(size=1, replace=FALSE)

select_player
```

```{r}
select_player_Batting <- Batting %>% 
  filter(playerID %in% select_player) %>% 
  select(playerID, player_index, yearID, year_index, Age, cAge, cAgeSq, AB, HR, p, park_index)

select_player_Batting
```

```{r}
#These first three effects (alpha, beta, and eta) are all corresponding to the 651st player (Robin Yount)
alpha_i651 <- fit.poly %>% 
  spread_draws(alpha[group]) %>% 
  summarise_draws() %>% 
  filter(group==651)

beta_i651 <- fit.poly %>% 
  spread_draws(beta[group]) %>% 
  summarise_draws() %>% 
  filter(group==651)

eta_i651 <- fit.poly %>% 
  spread_draws(eta[group]) %>% 
  summarise_draws() %>% 
  filter(group==651)

#Meanwhile, this value corresponds to the park
delta_i651 <- fit.poly %>% 
  spread_draws(delta[group]) %>% 
  summarise_draws() %>% 
  filter(group==24)

#And this value corresponds to the years that he played
xi_i651 <- fit.poly %>% 
  spread_draws(xi[group]) %>% 
  summarise_draws() %>% 
  filter(group >= 2 & group <= 21)
```

```{r}
#This outputs the associated means for each index for player 651
alpha_i651 %>% pull(mean)
beta_i651 %>% pull(mean)
eta_i651 %>% pull(mean)
delta_i651 %>% pull(mean)
xi_i651 %>% pull(mean)
```

```{r}
select_player_Batting <- select_player_Batting %>% 
  mutate(alpha = alpha_i651 %>% pull(mean), .after = player_index) %>%
  mutate(beta = beta_i651 %>% pull(mean), .after = cAge) %>% 
  mutate(eta = eta_i651 %>% pull(mean), .after = cAgeSq) %>% 
  mutate(delta = delta_i651 %>% pull(mean), .after = park_index) %>% 
  mutate(xi = xi_i651 %>% pull(mean), .after = year_index) %>% 
  mutate(pred = alpha + (beta*cAge) + (eta*cAgeSq) + (delta) + (xi) , .after = p) %>% 
  mutate(inv_logit_pred = inv.logit(pred), .after=pred)
```

```{r}
ggplot(data = select_player_Batting)+
  aes(x = cAge, y = p)+
  geom_point()+
  geom_smooth()+
  labs(title = "Actual Trajectory for player #651")
```

```{r}
ggplot(data = select_player_Batting)+
  aes(x = cAge, y=inv_logit_pred)+
  geom_point()+
  geom_smooth()+
  labs(title = "Predicted Career Trajectory for #651")
```
